---
title: "Models"
author: "Sophie Z"
format: html
execute: 
  echo: false
---
```{r}
 #| label: setup
 #| message: FALSE
 #| warnings: FALSE
suppressPackageStartupMessages({library(tidyverse)})
suppressPackageStartupMessages({library(brms)})
suppressPackageStartupMessages({library(tidybayes)})
library(gtsummary)
  
```

  
```{r}
#| label: model
#| cache: true
poll_data <- tibble(biden = c(rep(1, 655), 
                              rep(0, 904)))
 fit_bern <- brm(formula = biden ~ 1,
    data = poll_data,
    family = bernoulli(),
    refresh = 0,
    silent = 2,
    seed = 9)

```
 
```{r}
#| label: plot
ndata <-  tibble(.rows = 1)
fit_bern |>
  add_epred_draws(ndata) |>
    select(.epred) |>
      ggplot(aes(x = .epred)) + geom_density(y = after_stat(count/sum(count))) +
        scale_x_continuous(labels = scales::percent_format()) + scale_y_continuous(labels = scales::percent_format()) +
        labs(title = "Posterior Distribution for p", 
            subtitle = "There is a 95% chance for a value between XX and XX", 
            x = "Proportion, p, of red bead in urn", 
            y = "Probability")
```

 We have set up a quarto document and addressed what the preceptor table will look like. We know our data set is from a YouGov poll that polled 1,559 US citizens on 3/10-12/24. We are trying to answer using these resources, "what proportion of all votes will be cast for Joe Biden in the 2024 election?" We have developed a Population table and determined it's stability, though not it's representativeness and acknowledged that unconfoundedness is irrelevant. We are concerned on how representative the YouGov poll was, which may make an inaccurate prediction. We are using a Bernoulli model to model the data. The model is a predictive model that that shows binary outcomes. We then plotted it into a graph.  The QoI we seek is the section of the highest probabilites to occur though the extent of that Qol is unsure. The estimate is that he will recieve 42% of the vote, plus or minus 2.5%.
 
 $$ biden_i =  \mu + \epsilon_i $$

```{r}
tbl_regression(fit_bern, intercept = TRUE)
```
